---
title: "Type coercion"
author: "YOU"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

-   `c(1, 1L, "C")`
```{r}
c(1, 1L, "C")
```

```{r}
1
1L
"C"
```

```{r}
typeof(c(1, 1L, "C"))
```

I was right about this one, because it seems like if there's a character R will turn everything into a character. 

-   `c(1L / 0, "A")`

```{r}
c(1L / 0, "A")
```

```{r}
typeof(1L)
typeof(0)
typeof(1L/0)
typeof("A")
```

```{r}
typeof(c(1L / 0, "A"))
```

Double seems to be dominant over integer, but character is dominant over both. 

-   `c(1:3, 5)`

```{r}
c(1:3, 5)
```

```{r}
typeof(1:3)
typeof(5)
```

Not sure why 5 was double.

```{r}
typeof(c(1:3, 5))
```

But once again, double is dominant over integer. 

-   `c(3, "3+")`

```{r}
c(3, "3+")
```

```{r}
typeof(3)
typeof("3+")
```

```{r}
typeof(c(3, "3+"))
```

Got these right!

-   `c(NA, TRUE)`

```{r}
c(NA, TRUE)
```

```{r}
typeof(NA)
typeof(TRUE)
```

```{r}
typeof(c(NA, TRUE))
```

Got these right!

## References {#references}
1. Assignment Adapted from [Mine Cetinkaya-Rundel's Data Science in a Box](https://github.com/rstudio-education/datascience-box)